---
title: Template Title
subtitle: A subtitle for the paper
author:
  - name: Author Name
    email: author@example.com
    affiliations:
      - name: University
thanks: |
  The author thanks someone for helpful comments.
abstract: |
  This is a minimal example of the bjk-academic template rendered via Quarto.
  It demonstrates math, R code, theorem environments, and the bundled macros.
keywords:
  - template
  - example
date: today
date-format: long
bibliography: references.bib
format:
  academic-typst:
    section-numbering: "1.1.1"
    titlepage: true
    font-paths: ["static/fonts"]
execute:
  echo: false
  warning: false
---

# Introduction

This template supports LaTeX math. For example, a linear regression model:

$$
Y_i = \beta_0 + \beta_1 X_i + \varepsilon_i, \qquad \varepsilon_i \sim \mathcal{N}(0, \sigma^2).
$$ {#eq-regression}

An unlabelled display equation is not numbered:

$$
\sum_{i=1}^{n} (Y_i - \hat{Y}_i)^2.
$$

We refer to @eq-regression. The `def` macro highlights a defined term:
```{=typst}
#def[regression].
```
The draft `note` macro flags work in progress:
```{=typst}
#note[a note to self].
```

# Setup

```{=typst}
#assumption(title: "Regularity")[
  The errors $epsilon_i$ are independent with mean zero and finite variance.
] <assm-regularity>

#lemma(title: "Consistency")[
  Under @assm-regularity, the OLS estimator $hat(beta)$ is consistent.
] <res-consistency>

#proof[
  Standard Cauchy--Schwarz argument. #qedhere
]

#proposition[
  The OLS estimator achieves the Cramér--Rao bound under Gaussian errors.
] <res-efficiency>

#corollary[
  No unbiased estimator has smaller variance than #mathbf[hat(beta)].
]
```

```{=typst}
#paragraph[Discussion.]
```
The macro `deriv` produces a derivative: `#deriv($Y$, $X$)`. The partial form
is `#pderiv($Y$, $X_i$)`. Both render with the standard fraction style:
```{=typst}
$ deriv(Y, X) quad pderiv(Y, X_i) $
```

# Analysis

We fit a simple linear model of fuel efficiency on vehicle weight using the `mtcars` dataset, following @horst2020 and others [@katsushika1831].

```{r}
#| echo: true
fit <- lm(mpg ~ wt, data = mtcars)
summary(fit)
```

As @fig-mpg-wt shows, heavier cars tend to have lower fuel efficiency.

```{r}
#| label: fig-mpg-wt
#| fig-cap: |
#|   **Fuel efficiency vs. vehicle weight**.
#|   Points show individual cars from the mtcars dataset.
#|   The blue line is a linear fit with a 95% confidence band.
#| fig-width: 5
#| fig-height: 3.5

library(ggplot2)
library(cowplot)

p <- ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  geom_smooth(method = "lm", color = "steelblue") +
  labs(x = "Weight (1000 lbs)", y = "Miles per Gallon") +
  theme_cowplot()

p
```

{{< pagebreak >}}

{{< appendix >}}

# Restated lemma

```{=typst}
#theorion-restate(filter: <res-consistency>)

#proof[
  See textbook derivation.
]
```

<!-- Bibliography -->
